---
title: "Example"
output: word_document
date: '2022-07-15'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Connect to the AKFIN database and query the spiny dogfish relative population numbers in the Central GOA and East Yakutat/Southeast management areas
```{r query, echo=TRUE}

libs <- c('dplyr', 'tidyr', 'RODBC', 'ggplot2')
if(length(libs[which(libs %in% rownames(installed.packages()) == FALSE )]) > 0) {install.packages(libs[which(libs %in% rownames(installed.packages()) == FALSE)])}
lapply(libs, library, character.only = TRUE)

# Enter your username and password for the AKFIN database. Note that these credentials are different than what you may use to access AKFIN Answer. Contact AKFIN for more information.
username_akfin = 'my_username'
password_akfin = 'my_password'
channel_akfin <- odbcConnect("akfin", uid = username_akfin, pwd = password_akfin, believeNRows=FALSE)

dogfish <- sqlQuery(channel_akfin, query = ("
                select    *
                from      afsc_host.fiss_rpn
                where     species in ('Spiny dogfish') and fmp_sub_area in ('CGOA', 'EY/SE')
                ")) %>% 
  dplyr::rename_all(tolower) 
```

## Plot the IPHC survey relative population numbers for spiny dogfish
```{r plot, echo=TRUE}
ggplot(data = dogfish, aes(x = survey_year)) +
  geom_ribbon(aes(ymin = fmp_lci, ymax = fmp_uci), alpha = 0.2, col = NA) +
  geom_point(aes(y = fmp_rpn)) +
  geom_line(aes(y = fmp_rpn)) +
  facet_wrap(~fmp_sub_area) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = 'Year', y = 'RPN')
```

## Plot the number of total sets and sets with positive catch for spiny dogfish by depth strata in order to evaluate changes in sampling effort over time
```{r n, echo=TRUE}
nsum <- dogfish %>% 
         select(survey_year, rpn_strata,
                total = n_stations, pos_catch = n_pos_catch) %>% 
  tidyr::pivot_longer(cols = c('total', 'pos_catch'))

ggplot(data = nsum, aes(x = survey_year, y = value, lty = name, shape = name)) +
  geom_point() +
  geom_line() +
  facet_wrap(~rpn_strata, ncol = 2) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = 'Year', y = 'Number of sets')
```
